Simulation Study with Feature Contribution

### 2021-09-30 Simulation with Single Profile.Rmd
Adding updated paper drafts

@@

}

>>>>

```{r}
perplexity = 10

 xTSNE <- MultiPermanova(yes_structure_final[,1:20], maptype = "tSNE")
#  results_list[[j]] <- xTSNE

  df2 = tibble(Holdout = 1:length(xTSNE$modellist), PValues = sapply(xTSNE$modellist, pullPval), Fstat = sapply(xTSNE$modellist, pullFstat))
  df2$Colors <- ifelse(df2$PValues < 0.05, TRUE, FALSE)
  df2list[[j]] = df2
```

@@
